Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2022-01-19 FDT2020/response/response.tex

\response{The figure is moved to page 3.}
\item You mention that the Dom2IP algorithm can be used to prove that an IPs integrality gap is unbounded. How effective is this? \arash{need to think about this.}
\item Lemma 9 requires $\gamma_0 + \gamma_1 \leq 1$. Perhaps this should already be included
in Lemma 8.
\response{Fixed. Also added a constraint into the formulation of LPC that ensures $\lambda_0 + \lambda_1\leq 1$ and corresponding changes in the proof of the Claim.}
\item In the proof of Lemma 9, “We need to show that $\gamma_0\hat{x}^0_j + \gamma\hat{x}^1_j \leq gx'_j.$" has
an extra $g$ in it.
\response{Fixed.}
\item On page 13, “nodes in level $L_i$” should be “nodes in level $i$” and “points
in the leaves” should be just “leaves.” \response{Fixed.}
\item On page 24, “applying this tool . . . can be a tool” is redundant. \response{Fixed.}
\end{enumerate}

\subsection{Reviewer \#3}

\subsubsection{Main Comments}

\subsubsection{Detailed Comments}
\begin{itemize}
\item I’m attaching a file with line numbers. I strongly recommend for any future submission
using the lineno package, because it makes my job as a reviewer much easier. I will refer to
pairs (page number, line number) below.
\response{Thank you for the recommendation. We added line numbers to the document.}
\item (2,10) “we have formulated” – better to say “instances … are known” and give a reference, e.g. to MIPLIB; or if you have some particularly hard instances in mind that YOU have formulated, you can refer to them, but this should be a fairly widely known
fact. 
\response{MIPLIB citation added and the wording is changed as suggested.}

@@

\item (2,14) “the” -> “these”?
\item (2,26) “from the problem” – what problem? Maybe “using special problem structure together with the result of an LP relaxation to obtain an integer feasible solution
whose value is at most C times the value of the LP optimum” or something like that.
\response{Paragraph reworded as follows: Many combinatorial optimization problems can be formulated as IPs. An {\em LP-based approximation algorithm} uses the LP relaxations to the IP formulation to find provably good approximate feasible integer solutions in polynomial time. At the highest level, this involves solving the LP relaxation, using special  problem structure to find a feasible integer solution, and proving that the objective value of the solution is no more than $C$ times worse than the bound from the LP relaxation. The approximation factor $C$ can be a constant or depend on the input parameters of the IP, e.g. $O(\log(n))$ where $n$ is the number of variables in the formulation of the IP (the dimension of the problem).}

@@

\item (3,11) “it could not before” -> “they could not before”
\response{Fixed.}
\item (3,23) “ResearcherS”
\response{Fixed.}
\item (4,26) “We cannot hope to find…” – you’ve said this already. \response{The sentence was removed.}
\item (5,8) “express A vector” \response{Fixed.}
\item (5,10) Please define $[0,1]$ which appears in $[0,1]^k$ . It seems you mean the closed interval between 0 and 1, but it is very commonly also used to be the set $\{0,1\}$, so clarification is in order. \response{Added: , where $[0,1]^n = \{x\in \mathbb{R}^n, 0\leq x_i\leq 1 \mbox{ for } i\in[n]\}$ and $\{0,1\}^n = [0,1]^n \cap \mathbb{Z}^n$.}
\item (5,16) “of A blocking type” \response{Fixed.}
\item (5,23) “assuming” –> “under” \response{Fixed as suggested.}
\item (5,30) ”$S(I)\in \{0,1\}^n$ should be $\subseteq$ instead of $\in$ \response{Fixed.}
\item (6,1) delete “algorithm” \cite{Fixed.}
\item (6,3) “it would be optimal” - what is “it”? \response{Rephrased as follows: If $C = g(I)$, FDT would have been optimal.}

@@

\item (6,3) “we can only guarantee a factor of” I think it would be clearer to say “we can
only guarantee $C\leq g(I)$ ... ” \response{Fixed as suggested.}
\item (6,7) how does the $\min$ in $\min(Cx^*, {0,1}^n )$ work? Coordinate-wise, or?
\response{ Yes. But we removed this point-wise minimizing from the statement to make it simpler to state.}

@@

\response{Fixed.}
\item (7,5) what is $\chi^{F_i}$ ? I suppose it is the characteristic vector of $F_i$ but you should state
this clearly. Also, what is $E_x$ ? is it the number of edges of $x$, that is, $\mbox{supp}(x)|$? Again
please state clearly.  \response{We added definition of $E_x$ right before Theorem 6 and $\chi$ in the footnote of this page.}

@@

\item (7,13) “A subset of $U$ of $V$ ” – delete first “of”  
\response{Fixed.}
\item (7,18) define or comment on UG-hard \response{Added this in the footnote: UGC is short for Unique Game Conjecture and conjectured to be NP-hard [Khot2002]}

@@

\item (7,19) “feasbility” –> “feasibility”
\response{Fixed.}
\item (7,20) “3-5x slower” use “$\times$” (\\times) instead of “x”\response{Fixed.}
\item (7,29) Large space before “Note” - something fishy is going on here. \response{Fixed.}

### 2022-01-19 FDT2020/Introduction.tex
went through half of reviewer 3 minor comments

It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}. Given its practical importance, however, there are many commercial (e.g. CPLEX, GUROBI, XPRESS) and free (e.g. CBC) solvers that for specific IP instances can often find solutions that are optimal within a given tolerance. Still we have formulated moderate-sized IP instances that no commercial solver can currently solve. Thus there is value in heuristics to find feasible solutions for general IP instances (see e.g.~\cite{HanafiT2017}).
%For a generic IP instance $I$ it is NP-hard to even decide if the set of feasible solutions $S(I)$ is empty or not.
%There are a number of heuristics for this purpose, such as the
These heuristics, such as the popular Feasibility pump algorithm \cite{fp1,fp2}, are often effective and fast in practice. However, the heuristics can sometimes fail to find a feasible solution. Moreover, these heuristics do not provide any bounds on the quality of the solution they find.

@@

{\em LP-based approximation algorithms} use LP relaxations to find provably good approximate feasible solutions to IP problems in polynomial time. At the highest level, they involve solving the LP relaxation, using special structure from the problem to find a feasible solution, and proving that the objective value of the solution is no more than $C$ times worse than the bound from the LP relaxation. The approximation factor $C$ can be a constant or depend on the input parameters of the IP, e.g. $O(\log(n))$ where $n$ is the number of variables in the formulation of the IP (the dimension of the problem).

@@

If the integrality gap for an IP formulation is large, it is sometimes possible to add families of constraints to the formulation to reduce the integrality gap.  These constraints are redundant for the integer problem, but can make some fractional solutions no longer feasible for the LP. These families of constraints (cuts) can have exponential size (number of constraints) as long as we can provide a polynomial-time separation algorithm. A separation algorithm for a family of constraints takes an optimal solution to an LP instance that explicitly enforces only a (potentially empty) subset of the family. It either confirms that all constraints are satisfied or returns a most violated constraint. Thus one can add this constraint and repeat at most a polynomial number of times until all are satisfied.

Reducing the integrality gap of an IP formulation has two advantages.  It can lead to better LP-based approximation algorithm bounds as described above.  It can also help exact solvers run faster or solve instances it could not before. Exact IP solvers are based on intelligent branch-and-bound strategies.  As mentioned above, commercial and open-source MILP solvers can find exact solutions (or near-optimal solutions with a provable bound) to many specific instances of NP-hard combinatorial optimization problems. These solvers use the LP relaxation to get lower bounds (for minimization problems).  The search requires exponential time in the worst case. But this search is practically feasible when the solver can prune large amounts of the search space.  This happens when the lower bound for a region of the search space (subproblem) is worse than the value of a known feasible solution.  This requires a way to find a good heuristic solution and it requires good lower bounds that are as close to the actual optimal value of an IP subproblem as possible.

In this paper, we give a method to find feasible solutions for IPs if the integrality gap is bounded. The method is also a tool for evaluating the integrality gap for a formulation.  Researcher can use it to determine whether they should expend effort to find new classes of cuts.  They can also use it to help guide theory for finding tighter bounds on the integrality gap for classic problems like the traveling salesman problem.

@@

The value of $g(I)$ depends on the constraints in~(\ref{S}).  We cannot hope to find solutions for the IP with objective values better than $g(I)\cdot z_{LP}(I,c)$. More generally we can define the integrality gap for a class of instances $\mathcal{I}$ as follows.% In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}\label{gapproblem}
g(\mathcal{I}) = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}.
\end{equation}
For example, the integrality gap of the subtour-elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}. Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation to bound the quality of a feasible solution.

Our methods apply theory connecting integrality gaps to sets of feasible solutions. Instances $I$ with $g(I)=1$ have $P(I)=\conv(S(I))$, the convex hull of the lattice of feasible points. In this case, $P(I)$ is an \textit{integral} polyhedron. The spanning tree polytope of graph $G$, $\st(G)$, and the perfect-matching polytope of graph $G$, $\permat(G)$, have this property (\cite{Edmonds2003,edmondsPM}). Thus the linear-programming relaxation for minimum-cost spanning tree has basic feasible solutions (vertices) that are integral solutions, i.e. spanning trees. For such problems there is an algorithm to express vector $x\in P(I)$ (a feasible LP solution) as a convex combination of points in $S(I)$ (feasible IP solutions) in polynomial time \cite{cons-cara}.
% The number of feasible solutions ($k$) in the convex combination can vary by instance.
%\cindy{Should this proposition just be a corollary of the Carr-Vempala theorem?  Are we going to describe how to do it?  If so, there should be a forward pointer to that discussion.}

@@

For the case when $g(I)>1$ a similar statement is as follows. The {\em dominant} of $P(I)$, which we denote by $\dom(P(I))$, is the set of points $x'$ such that there exists a point $x\in P$ with $x'\geq x$ in every component. A polyhedron is of \textit{blocking type} if it is equal to its dominant.

@@

If we relax Question \ref{question1} (resp. Question \ref{question2}), but multiplying $g(I)$ (resp. $g(\mathcal{I})$) by a factor $C$, they are still very interesting, since they will provide upper bounds on the integrality gap of the instance (resp. the problem). The results in this paper serve this purpose.
\fi
To study integrality gaps, we wish to decompose a suitably scaled linear-programming solution into a convex combination of feasible integer solutions {\bf constructively}.  That is, we ask: assuming reasonable complexity assumptions, given a specific problem $\mathcal{I}$ with  $1<g(\mathcal{I})<\infty$, and $x\in P(I)$ for some $I\in \mathcal{I}$, \textbf{can we write} $Cx$ as a convex combination of points in $\dom(S(I))$? We wish to find the smallest factor $C$ possible.

@@

We give a general approximation framework for solving binary IPs.
Consider the set of points described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume in addition that $S(I)\in \{0,1\}^n$ and $P(I)\subseteq [0,1]^n$.
%\cindy{Is it $S(I) \subseteq \{0,1\}^n$?}
For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $x\in P(I)$, let the {\em support} of $x$ be $\spp(x)= \{i \in [n]: x_i \neq 0\}$. For an integer $\beta$ let $\{\beta\}^n$ be the vector $y\in \mathbb{R}^n$ with $y_i=\beta$ for $i\in [n]$.

In Section~\ref{sec:binaryfdt} we introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which is polynomial time algorithm. Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated coordinatewise by a ``factor" $C$ times $x$.
% in the coordinates corresponding to $x$.
If $C = g(I)$, it would be optimal. However we can only guarantee a factor of $g(I)^{|\spp(x)|}$. FDT iteratively solves linear programs that are about the same size as the description of $P(I)$.

@@

One can extend the FDT algorithm for binary IPs into covering\footnote{A covering IP has nonnegative constraint matrix, objective coefficients and right-hand side ($A,b,c$).} $\{0,1,2\}$ IPs by losing a factor $2^{|\spp(x)|}$ on top of the loss for FDT. To eradicate this extra factor, we must treat the coordinate $i$ with $x_i=1$ differently. In Section~\ref{sec:2EC} we focus on the 2-edge-connected multi-subgraph graph problem (2EC) defined above.  Its subtour-elimination LP relaxation is given in (\ref{eq:subtour}).
%}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^{E}_{\geq 0}$ find a 2-edge-connected multi-subgraph of $G$ with minimum cost. The natural linear programming relaxation for this problem is 
%\begin{equation}
%\min \{cx \; : \; x(\delta(U))\geq 2 \; \text{ for }\emptyset \subset U \subset V, \; x\in [0,2]^E\}
%\end{equation}
For input graph $G$, let $\subtour(G)$ denote the feasible region of this LP. Let $\2ec(G)$ be the convex hull of incidence vectors\footnote{The incidence vector $x$ of a 2-edge-connected multi-subgraph has an element for each edge $e$, with $x_e \in \{0,1,2\}$ indicating the number of times edge $e$ appears in the solution.} of 2-edge-connected multi-subgraphs of graph $G$. Following the definition in (\ref{gapproblem}) have
\begin{equation}
g(\2ec) = \sup_{c\geq 0 , G}\frac{\min_{x\in \2ec(G)} cx}{\min_{x\in \subtour(G)} cx}.
\end{equation}

For a multi-subset of edges $F$ of $E$, we use $\chi^F$ to denote the characteristic vector of $F$ which is a vector in $\mathbb{R}^E$ where $\chi^F_e$ is equal to the multiplicity of edge $e$ in $F$. We denote $E_x$ to denote $\spp(x)$ as a subset of edges of $E$.

@@

In the \textsc{minimum vertex cover problem (VC)} we are given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$. A subset of $U$ of $V$ is a \textit{vertex cover} if for all $e\in E$ at least one endpoint of $e$ is in $U$. The goal in VC is to find the minimum-cost vertex cover. The linear-programming relaxation for VC is
\begin{equation}
\min \{cx \; : \; x_u + x_v \geq	 1 \text{ for all } e=uv \in E, \; x\in [0,1]^{V}\}.
\end{equation}
The integrality gap of this formulation is exactly 2 \cite{davids}. Austrin, Khot and Safra~\cite{UGhardVC} show that it is UG-hard to approximate VC within any factor strictly better than 2. We compare  FDT and the feasbility pump heuristic \cite{fp1} on the small instances of the PACE\footnote{ Parameterized Algorithms and Computational Experiments: \url{https://pacechallenge.org/2019/}} 2019 challenge test cases \cite{PACE}. FDT was 3-5x slower, but still ran in seconds. It always gave a better vertex cover. For some instances the FDT solution's relative gap with respect to the optimal was half that of feasibility pump.
\subsubsection{Tree augmentation problem}
In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a spanning tree $T$ of $G$ and a cost vector $c\in \mathbb{R}^{E\setminus T}_{\geq 0}$. A subset $F$ of $E\setminus T$ is called a \textit{feasible augmentation} if $(V,T\cup F)$ is a 2-edge-connected graph. In TAP we seek the minimum cost feasible augmentation. The natural linear-programming relaxation for TAP is 
\begin{equation}\label{eq:cutLP}
\min \{cx\; : \; \sum_{\ell \in \cov(e)} x_{\ell} \geq 1 \text{ for } e\in T, \; x\in [0,1]^{E\setminus T}\}.
\end{equation}
where $\cov(e)$ for $e \in T$ is the set of edges $\ell \in E\setminus T$ such that $e$ is in the unique cycle of $T\cup \{\ell\}$. Another way to think of $\cov(e)$ is that if we remove edge $e$ from tree $T$, this partitions the vertices into two connected sets $U$ and $V-U$.  Then $\cov(e) = \delta(U)$ is the set of edges $\ell \neq e$ that cross the cut between $U$ and $V-U$, and whose addition would reconnect the tree. We call the LP above the cut LP. The integrality gap of the cut LP is known to be between $\frac{3}{2}$ \cite{32gaptap} and $2$ \cite{FJ81}. We create random fractional extreme points of the cut LP and apply FDT to find integral solutions. For our instances, the ratio of the value of the feasible solution to the LP lower bound is always below $\frac{3}{2}$. This provides evidence that the integrality gap for such instances may be less than $\frac{3}{2}$.

@@

%\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?} \cindy{Yes that would be fine, if the reader could also use that figure then.  They could page forward to see the figure when reading the introduction.}
%\arash{I changed the paragraph below a little bit, can you check?} \cindy{Looks good. I just changed one sentence to the active voice.  If you're OK with that, you can delete these 2 comments. Thanks!}
Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point. Multiple groups of researchers have conjectured that $g(\2ec)\leq \frac{6}{5}$ (see \cite{alexander2006integrality,boydlegault,hn19}, but the only known upper bound on $g(\2ec)$ stands at $\frac{3}{2}$ \cite{wolsey}. We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges, thereby confirming the conjecture for these instances.\cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.

\cindy{We probably need an explicit list of contributions.  It could be another subsection of the introduction.  This will help the reviewer and eventually, if published, the reader.}
\subsection{Contribution summary}
In summary, this papers's contributions are:
\begin{itemize}
\item We give an algorithm to express any feasible point for the LP relaxation of a binary IP
%(or a \{0,1,2\} IP) 
as a convex combination of feasible solutions, provided the IP integrality gap is bounded.  This is the Fractional Decomposition Tree (FDT) algorithm.
\item We give a simple  algorithm to give a feasible solution for any binary IP with bounded integrality gap. If this algorithm fails, then the integrality gap is infinite.
\item We experimentally show that FDT can give good approximate solutions to small instances of vertex-cover and tree augmentation problems.
\item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for integrality gap for 2EC for these instances.
\item We demonstrate (with 2EC) how FDT exeriments can support theoretical work on integrality gaps for specific problems. In particular, we computationally prove an upper bound on small instances of 2EC with a specific structure.
\end{itemize}

>>>>

It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}. Given its practical importance, however, there are many commercial (e.g. CPLEX, GUROBI, XPRESS) and free (e.g. CBC) solvers that for specific IP instances can often find solutions that are optimal within a given tolerance. Still there are known moderate-sized IP instances that no commercial solver can currently solve \cite{MIPLIB}. Thus there is value in heuristics to find feasible solutions for general IP instances (see e.g.~\cite{HanafiT2017}).
%For a generic IP instance $I$ it is NP-hard to even decide if the set of feasible solutions $S(I)$ is empty or not.
%There are a number of heuristics for this purpose, such as the
These heuristics, such as the popular Feasibility pump algorithm \cite{fp1,fp2}, are often effective and fast in practice. However, the heuristics can sometimes fail to find a feasible solution. Moreover, these heuristics do not provide any bounds on the quality of the solution they find.

@@

Many combinatorial optimization problems can be formulated as IPs. An {\em LP-based approximation algorithm} uses the LP relaxations to the IP formulation to find provably good approximate feasible integer solutions in polynomial time. At the highest level, this involves solving the LP relaxation, using special  problem structure to find a feasible integer solution, and proving that the objective value of the solution is no more than $C$ times worse than the bound from the LP relaxation. The approximation factor $C$ can be a constant or depend on the input parameters of the IP, e.g. $O(\log(n))$ where $n$ is the number of variables in the formulation of the IP (the dimension of the problem).

@@

If the integrality gap for an IP formulation is large, it is sometimes possible to add families of constraints to the formulation to reduce the integrality gap.  These constraints are redundant for the integer problem, but can make some fractional solutions no longer feasible for the LP. These families of constraints (cuts) can have exponential size (number of constraints) as long as we can provide a polynomial-time separation algorithm. A separation algorithm for a family of constraints takes an optimal solution to an LP instance that explicitly enforces only a (potentially empty) subset of the family. It either confirms that all constraints are satisfied or returns a violated constraint. Thus one can add this constraint and repeat at most a polynomial number of times until all are satisfied.

Reducing the integrality gap of an IP formulation has two advantages.  It can lead to better LP-based approximation algorithm bounds as described above.  It can also help exact solvers run faster or solve instances they could not before. Exact IP solvers are based on intelligent branch-and-bound strategies.  As mentioned above, commercial and open-source MILP solvers can find exact solutions (or near-optimal solutions with a provable bound) to many specific instances of NP-hard combinatorial optimization problems. These solvers use the LP relaxation to get lower bounds (for minimization problems).  The search requires exponential time in the worst case. But this search is practically feasible when the solver can prune large amounts of the search space.  This happens when the lower bound for a region of the search space (subproblem) is worse than the value of a known feasible solution.  This requires a way to find a good heuristic solution and it requires good lower bounds that are as close to the actual optimal value of an IP subproblem as possible.

In this paper, we give a method to find feasible solutions for IPs if the integrality gap is bounded. The method is also a tool for evaluating the integrality gap for a formulation.  Researchers can use it to determine whether they should expend effort to find new classes of cuts.  They can also use it to help guide theory for finding tighter bounds on the integrality gap for classic problems like the traveling salesman problem.

@@

The value of $g(I)$ depends on the constraints in~(\ref{S}). More generally we can define the integrality gap for a class of instances $\mathcal{I}$ as follows.% In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}\label{gapproblem}
g(\mathcal{I}) = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}.
\end{equation}
For example, the integrality gap of the subtour-elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}. Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation to bound the quality of a feasible solution.

Our methods apply theory connecting integrality gaps to sets of feasible solutions. Instances $I$ with $g(I)=1$ have $P(I)=\conv(S(I))$, the convex hull of the lattice of feasible points. In this case, $P(I)$ is an \textit{integral} polyhedron. The spanning tree polytope of graph $G$, $\st(G)$, and the perfect-matching polytope of graph $G$, $\permat(G)$, have this property (\cite{Edmonds2003,edmondsPM}). Thus the linear-programming relaxation for minimum-cost spanning tree has basic feasible solutions (vertices) that are integral solutions, i.e. spanning trees. For such problems there is an algorithm to express a vector $x\in P(I)$ (a feasible LP solution) as a convex combination of points in $S(I)$ (feasible IP solutions) in polynomial time \cite{cons-cara}.
% The number of feasible solutions ($k$) in the convex combination can vary by instance.
%\cindy{Should this proposition just be a corollary of the Carr-Vempala theorem?  Are we going to describe how to do it?  If so, there should be a forward pointer to that discussion.}

@@

For the case when $g(I)>1$ a similar statement is as follows. The {\em dominant} of $P(I)$, which we denote by $\dom(P(I))$, is the set of points $x'$ such that there exists a point $x\in P$ with $x'\geq x$ in every component. A polyhedron is of \textit{a blocking type} if it is equal to its dominant.

@@

If we relax Question \ref{question1} (resp. Question \ref{question2}), but multiplying $g(I)$ (resp. $g(\mathcal{I})$) by a factor $C$, they are still very interesting, since they will provide upper bounds on the integrality gap of the instance (resp. the problem). The results in this paper serve this purpose.
\fi
To study integrality gaps, we wish to decompose a suitably scaled linear-programming solution into a convex combination of feasible integer solutions {\bf constructively}.  That is, we ask: under reasonable complexity assumptions, given a specific problem $\mathcal{I}$ with  $1<g(\mathcal{I})<\infty$, and $x\in P(I)$ for some $I\in \mathcal{I}$, \textbf{can we write} $Cx$ as a convex combination of points in $\dom(S(I))$? We wish to find the smallest factor $C$ possible.

@@

We give a general approximation framework for solving binary IPs.
Consider the set of points described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume in addition that $S(I)\subseteq  \{0,1\}^n$ and $P(I)\subseteq [0,1]^n$, where $[0,1]^n = \{x\in \mathbb{R}^n, 0\leq x_i\leq 1 \mbox{ for } i\in[n]\}$ and $\{0,1\}^n = [0,1]^n \cap \mathbb{Z}^n$.
%\cindy{Is it $S(I) \subseteq \{0,1\}^n$?}
For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $x\in P(I)$, let the {\em support} of $x$ be $\spp(x)= \{i \in [n]: x_i \neq 0\}$. For an integer $\beta$ let $\{\beta\}^n$ be the vector $y\in \mathbb{R}^n$ with $y_i=\beta$ for $i\in [n]$.

In Section~\ref{sec:binaryfdt} we introduce the \textit{Fractional Decomposition Tree} (FDT) which is polynomial time algorithm. Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated coordinatewise by a ``factor" $C$ times $x$.
% in the coordinates corresponding to $x$.
If $C = g(I)$, FDT would have been optimal. However we can only guarantee $C\leq g(I)^{|\spp(x)|}$. FDT iteratively solves linear programs that are about the same size as the description of $P(I)$.

@@

One can extend the FDT algorithm for binary IPs into covering\footnote{A covering IP has nonnegative constraint matrix, objective coefficients and right-hand side ($A,b,c$).} $\{0,1,2\}$ IPs by losing a factor $2^{|\spp(x)|}$ on top of the loss for FDT. To eradicate this extra factor, we must treat the coordinate $i$ with $x_i=1$ differently. In Section~\ref{sec:2EC} we focus on the 2-edge-connected multi-subgraph graph problem (2EC) defined above.  Its subtour-elimination LP relaxation is given in (\ref{eq:subtour}).
%}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^{E}_{\geq 0}$ find a 2-edge-connected multi-subgraph of $G$ with minimum cost. The natural linear programming relaxation for this problem is 
%\begin{equation}
%\min \{cx \; : \; x(\delta(U))\geq 2 \; \text{ for }\emptyset \subset U \subset V, \; x\in [0,2]^E\}
%\end{equation}
For input graph $G$, let $\subtour(G)$ denote the feasible region of this LP. Let $\2ec(G)$ be the convex hull of incidence vectors\footnote{The incidence vector of a 2-edge-connected multi-subgraph $F$, denoted by $\chi^F$ has an element for each edge $e$, with $x_e \in \{0,1,2\}$ indicating the number of times edge $e$ appears in the solution.} of 2-edge-connected multi-subgraphs of graph $G$. Following the definition in (\ref{gapproblem}) have
\begin{equation}
g(\2ec) = \sup_{c\geq 0 , G}\frac{\min_{x\in \2ec(G)} cx}{\min_{x\in \subtour(G)} cx}.
\end{equation}

We denote $E_x$ when regarding to $\spp(x)$ as a subset of edges of $E$.

@@

In the \textsc{minimum vertex cover problem (VC)} we are given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$. A subset $U$ of $V$ is a \textit{vertex cover} if for all $e\in E$ at least one endpoint of $e$ is in $U$. The goal in VC is to find the minimum-cost vertex cover. The linear-programming relaxation for VC is
\begin{equation}
\min \{cx \; : \; x_u + x_v \geq	 1 \text{ for all } e=uv \in E, \; x\in [0,1]^{V}\}.
\end{equation}
The integrality gap of this formulation is exactly 2 \cite{davids}. Austrin, Khot and Safra~\cite{UGhardVC} show that it is UGC-hard to approximate VC within any factor strictly better than 2\footnote{UGC is short for Unique Game Conjecture and conjectured to be NP-hard \cite{Khot2002OnTP}}. We compare  FDT and the feasibility pump heuristic \cite{fp1} on the small instances of the PACE\footnote{ Parameterized Algorithms and Computational Experiments: \url{https://pacechallenge.org/2019/}} 2019 challenge test cases \cite{PACE}. FDT was $3$-$5\times$ slower, but still ran in seconds. It always gave a better vertex cover. For some instances the FDT solution's relative gap with respect to the optimal was half that of feasibility pump.
\subsubsection{Tree augmentation problem}
In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a spanning tree $T$ of $G$ and a cost vector $c\in \mathbb{R}^{E\setminus T}_{\geq 0}$. A subset $F$ of $E\setminus T$ is called a \textit{feasible augmentation} if $(V,T\cup F)$ is a 2-edge-connected graph. In TAP we seek the minimum cost feasible augmentation. The natural linear-programming relaxation for TAP is 
\begin{equation}\label{eq:cutLP}
\min \{cx\; : \; \sum_{\ell \in \cov(e)} x_{\ell} \geq 1 \text{ for } e\in T, \; x\in [0,1]^{E\setminus T}\}.
\end{equation}
where $\cov(e)$ for $e \in T$ is the set of edges $\ell \in E\setminus T$ such that $e$ is in the unique cycle of $T\cup \{\ell\}$. Another way to think of $\cov(e)$ is that if we remove edge $e$ from tree $T$, this partitions the vertices into two connected sets $U$ and $V-U$.  Then $\cov(e) = \delta(U)$ is the set of edges $\ell \neq e$ that cross the cut between $U$ and $V-U$, and whose addition would reconnect the tree. We call the LP above the cut LP. The integrality gap of the cut LP is known to be between $\frac{3}{2}$ \cite{32gaptap} and $2$ \cite{FJ81}. We create random fractional extreme points of the cut LP and apply FDT to find integral solutions. For our instances, the ratio of the value of the feasible solution to the LP lower bound is always below $\frac{3}{2}$. This provides evidence that the integrality gap for such instances may be less than $\frac{3}{2}$.

@@

%\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?} \cindy{Yes that would be fine, if the reader could also use that figure then.  They could page forward to see the figure when reading the introduction.}
%\arash{I changed the paragraph below a little bit, can you check?} \cindy{Looks good. I just changed one sentence to the active voice.  If you're OK with that, you can delete these 2 comments. Thanks!}
Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point. Multiple groups of researchers have conjectured that $g(\2ec)\leq \frac{6}{5}$ (see \cite{alexander2006integrality,boydlegault,hn19}, but the only known upper bound on $g(\2ec)$ stands at $\frac{3}{2}$ \cite{wolsey}. We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges, thereby confirming the conjecture for these instances. Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.
\cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}
\cindy{We probably need an explicit list of contributions.  It could be another subsection of the introduction.  This will help the reviewer and eventually, if published, the reader.}
\subsection{Contribution summary}
In summary, this papers's contributions are:
\begin{itemize}
\item We give an algorithm to express any feasible point for the LP relaxation of a binary IP
%(or a \{0,1,2\} IP) 
as a convex combination of feasible solutions, provided the IP integrality gap is bounded.  This is the Fractional Decomposition Tree (FDT) algorithm.
\item We give a simple  algorithm to give a feasible solution for any binary IP with bounded integrality gap. If this algorithm fails, then the integrality gap is infinite.
\item We experimentally show that FDT can give good approximate solutions to small instances of vertex-cover and tree augmentation problems.
\item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for integrality gap for 2EC for these instances.
\item We demonstrate (with 2EC) how FDT exeriments can support theoretical work on integrality gaps for specific problems. In particular, we computationally prove an upper bound on small instances of 2EC with a specific structure.
\end{itemize}
